Enabling GPU Virtualization in Cloud Environments

### 2016-02-04 paper.tex
agradecimientos de la UPV

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Gustavo Edo and Vicente Roca for their help.

This research was supported by Universitat Jaume~I research project (P11B2013-21); and project
TIN2014-53495-R from MINECO and FEDER.

\bibliographystyle{apalike}
{\small
\bibliography{paper}}

>>>>

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Gustavo Edo and Vicente Roca for their help.
This research was supported by Universitat Jaume~I research project (P11B2013-21); and project
TIN2014-53495-R from MINECO and FEDER.
The initial version of rCUDA was jointly developed by Universitat Polit\`ecnica de 
Val\`encia (UPV) and Universitat Jaume I de Castell\'on (UJI) until year 2010. 
This initial development was later split into two branches. Part of the 
UPV version was used in this paper. The development of the UPV branch 
was supported by Generalitat Valenciana under Grants PROMETEO 2008/060 
and Prometeo II 2013/009. 
\bibliographystyle{apalike}
{\small
\bibliography{paper}}
